### 2025-06-18 index.qmd
20250618 - add package for fitting skew-normal distribution

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", "data.table", 
  "future", "future.apply"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "sn", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", "data.table", 
  "future", "future.apply", "SimDesign"
)

### 2025-06-18 simulation.qmd
20250618 - add package for fitting skew-normal distribution

```{r}
library("ffanalytics")
library("data.table")
library("future")
library("future.apply")
library("progressr")
library("SimDesign")
library("tidyverse")
```

>>>>

```{r}
library("ffanalytics")
library("data.table")
library("future")
library("future.apply")
library("progressr")
library("SimDesign")
library("fitdistrplus")
library("sn")
library("tidyverse")
```
